The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-08-02 manuscript/manuscript.tex
Before sharing to John

Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., stellar mass \smass, luminosity \lhost) suggest an evolutionary connection. A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates. For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ image, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting. The black hole mass (\mbh) is determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators. We find that the  {\it observed} ratio of \mbh/\smass~is larger at $z\sim1.5$ by a factor of $\sim2.2$ as compared to that in the local universe, while the scatter is as low as in the local universe. However, when accounting for selection effects (estimated using two independent and complementary methods), we find that no-evolution is consistent with the data at the 95\% CL, both using our sample by itself and in combination with literature data. The relationship between \mbh\ and host galaxy total luminosity paints a similar picture. Therefore, given the uncertainties, our results are in agreement with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter. Using a mass-matched sample of inactive galaxies to infer the bulge-to-total mass fraction we show that the bulge \mbh/\bmass~relation is significantly offset from the local one by a factor of $\sim$$+5.5$; this offset is still present even after accounting for selection effects. Thus, our observations are consistent with a scenario in which stellar mass is transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than the mass accretion onto the SMBH.

>>>>

Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., stellar mass \smass, luminosity \lhost) suggest an evolutionary connection. A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates. For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ image, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting. The black hole mass (\mbh) is determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators. We find that the  {\it observed} ratio of \mbh/\smass~is larger at $z\sim1.5$ by a factor of $\sim2.2$ as compared to that in the local universe, while the scatter is as low as in the local universe. However, when accounting for selection effects (estimated using two independent and complementary methods), we find that no-evolution is consistent with the data at the 95\% CL, both using our sample by itself and in combination with literature data. The relationship between \mbh\ and host galaxy total luminosity paints a similar picture. Therefore, given the uncertainties, our results are in agreement with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter. Using a mass-matched sample of inactive galaxies to infer the bulge-to-total mass fraction we show that the bulge \mbh/\bmass~relation is significantly offset from the local one by a factor of $\sim$$+5.5$; % 5.5 = 10^(1.86*log(2.5))
this offset is still present even after accounting for selection effects. Thus, our observations are consistent with a scenario in which stellar mass is transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than the mass accretion onto the SMBH.
